Typed Functional Genetic Programming

### 2013-07-13 tex/thesis.tex
[tex]

\chapter{Definitions}

	\Lets first say some basic definitions.

\section{Genetic Programming}
\label{GP}

@@

\subsection{Program trees}

@@

\subsection{Building blocks}
\label{building-blocks}

@@

\subsection{Generating individual}
\label{GPgene}

@@

\subsection{Selection}

@@

\subsection{Crossover}

@@

\subsection{Reproduction}

@@

\subsection{Mutation}

@@

\subsection{Construction of a next population}

@@

\newpage
\subsection{GP algorithm in pseudocode}

@@

\newpage		
\section{Lambda term}
\label{deflam}

@@

\chapter{ Our approach }

@@

\begin{todo}
Mužem na to koukat jako na takovou tu redukci simetrií, 
najít to v AIAMA a pořádně popsat.
\end{todo}

@@

\begin{todo}
 & Internal state
 & Edge selection model

>>>>

\chapter{Genetic Programming}
\label{GP}

@@

\section{Program trees}

@@

\section{Building blocks}
\label{building-blocks}

@@

\section{Generating individual}
\label{GPgene}

@@

\section{Selection}

@@

@@

\section{Reproduction}

@@

@@

\section{Construction of a next population}

@@

\newpage
\section{GP algorithm in pseudocode}

@@

\chapter{Mathematical background}

\begin{todo}
 & Shrnout tu nějak ve skratce tuhle kapitolu.. 
\end{todo}

\section{Lambda term}
\label{deflam}

@@

\chapter{ Design of our system }

@@

%\begin{todo}
%Mužem na to koukat jako na takovou tu redukci simetrií, 
%najít to v AIAMA a pořádně popsat.
%\end{todo}

@@

Now we will describe further modification of the A* algorithm 
which is generalizing it enough to enable use of \textit{ramped half-and-half}
term generating method and other term generating methods.

\begin{enum}
	& Co se přidalo 
	  && strategy
	     &&& selectedNexts
	  && outer while loop 	
\end{enum}

\Pseudokod{A*-with-strategy( start , n , isGoal , heuristic , strategy )}{

	$results \la$ empty set\;\;

	\While{ $\vert results \vert < n$ }{

		$open    \la$ empty priority queue \;
		$strategy.init()$\;\;

			$nexts \la strategy.filter$( $state$.nexts() , $state$.depth() ) \;\;

			\For{$next \in nexts$ }{
				$next$.G $\la $state$.G + 1$ \;
				$next$.F $\la $next$.G + heuristic$( $next$ )  \;
				$open$.insert( $next$ )\;			
			}
		}\;

	}

\begin{todo}
 & Internal state
 & Edge selection model
\end{todo}
